An emerging approach for cloud correction and filtering of operational microwave humidity radiances

### 2020-09-11 Article/ici_submm_cloudcorr.tex
Article: sectioning outline and new text

\title{An approach for cloud correction of operational humidity channels}

@@

\introduction
%
\todo{Add references and do a literature search on cloud filtering}

Satellite observations of humidity inside the troposphere are mainly performed
by downward-looking sensors. Among this class of observations, the frequency
range around 183\,GHz has a special position. Water vapour has a noticeable
transition at 22\,GHz, but it is relatively weak and only column values can be
derived \citep[e.g.][]{schluessel1990atmospheric} for the observation geometry
of concern. The first transition in the microwave region that can be used to
derive altitude information, i.e.\ can be used for ``sounding'', is the one at
183.31\,GHz \citep{kakar1983retrieval,wang1983profiling}. On the other hand, at
infrared wavelengths a high number of water vapour transitions are found,
including some of high strength. As a consequence, infrared sounders can
provide humidity profiles with high precision and good vertical resolution, but
with strong limitions imposed by clouds. To be able to also sense humidity
inside and below clouds weather satellites are since some time equipped with
channels around 183\,GHz. Today such channels are part of several sensors, such
as ATMS (Advanced Technology Microwave Sounder, \citet{weng2012introduction}).

@@

The main motivation for introducing 183\,GHz channels in operational sensors is
numerical weather prediction (NWP). Usage of microwave data by ``all-sky''
assimilation is growing \citep{geer2017growing}, but 183\,GHz data are still
mainly used in a clear sky fashion \citep{geer2018all}. The later is
particularly true in NWP of regional scope, all-sky assimilation of 183\,GHz at
many national weather agencies will likely not be reached in many years. The
cloud filtering in NWP differs between centres. One approach is to make use of
a ``scattering index'' \citep{bennartz2002precipitation}, based on the
observations alone. Today likely more common is to use ``observation minus
background'' (O-B), where the forecast model is used to obtain an estimate of
the expected clear-sky value and the observation is rejected if the deviation
exceeds some threshold (???). In both cases, the filtering typically involving
observations around 89 and/or 150\,GHz.

@@

All above filtering ...

\section{Data and methods}

>>>>

\title{An emerging approach for cloud correction and filtering of operational
  microwave humidity radiances}

@@

\introduction
%
Satellite observations of humidity inside the troposphere are mainly performed
by downward-looking sensors. Among this class of observations, the frequency
range around 183\,GHz has a special position. Water vapour has a noticeable
transition at 22\,GHz, but it is relatively weak and only column values can be
derived \citep[e.g.][]{schluessel1990atmospheric} for the observation geometry
of concern. The first transition in the microwave region that can be used to
derive altitude information, i.e.\ can be used for ``sounding'', is the one at
183.31\,GHz \citep{kakar1983retrieval,wang1983profiling}. On the other hand, at
infrared wavelengths a high number of water vapour transitions are found,
including some of high strength. As a consequence, infrared sounders can
provide humidity profiles with high precision and good vertical resolution, but
with strong limitions imposed by clouds. To be able to also sense humidity
inside and below clouds weather satellites are since some time equipped with
channels around 183\,GHz. Today such channels are part of several sensors, such
as ATMS (Advanced Technology Microwave Sounder, \citet{weng2012introduction}).

@@

The main motivation for introducing 183\,GHz channels in operational sensors is
numerical weather prediction (NWP). Usage of microwave data by ``all-sky''
assimilation is growing \citep{geer2017growing}, but 183\,GHz data are still
mainly used in a clear sky fashion \citep{geer2018all}. The later is
particularly true in NWP of regional scope, all-sky assimilation of 183\,GHz at
many national weather agencies will likely not be reached in many years. The
cloud filtering in NWP differs between centres. One approach is to make use of
a ``scattering index'' \citep{bennartz2002precipitation}, based on the
observations alone. Today, likely more common is to use ``observation minus
background'' (O-B), where the forecast model is used to obtain an estimate of
the expected clear-sky value and the observation is rejected if the deviation
exceeds some threshold (???). In both cases, the filtering typically involving
observations around 89 and/or 150\,GHz.

Despite the broad usage these filtering methods have some drawbacks. For
183\,GHz, the impact of hydrometeors systematically cause a decrease in the
observed radiance (maybe with exceptions at extremely dry conditions), see
e.g.\ \citet{barlakas:three:20} and below. This means that if any cloud
contaminated is missed by the filtering this will cause a negative bias in mean
radiance, compared to the true clear-sky mean. This bias will translate to
a bias in humidity after the retrieval or assimilation. The alternative is to
apply a very strict filtering, but this will result in that a high fraction of
actually clear-sky values will be rejected \todo{(Reka or better reference)},
i.e.\ an important loss of useful data. One for all. Same or lower frequency ...

@@

\newpage

\section*{Outline of sectioning}

2 Data and methods

2.1 Satellite sensors

2.1.1 Ice Cloud Imager (ICI)

2.1.2 Microwave Imager (MWI)

2.1.3 Arctic Weather Satellite (AWS)

2.2 Quantile Regression Neural Network (QRNN)

2.2.1 Theory

2.2.2 Evaluation metrics

2.3 Simulations

2.3.1 Input data

2.3.2 Simulation setup

2.3.3 Produced dataset
(If diifers between ICI, MWI and AWS, clarify this)

\noindent 3 Results

Short recap of aim of correction. We also use the correction as a filter, using
a threshold on the correction. We use 5K (?) threshold as example.

3.1 QRNN network configurations and training

3.2 ICI

3.2.1 Example results

Show a few estimated posterior distributions (one figure) and distribution of
predicted values (Fig 2)

3.2.2 Error of best estimate

3.2.3 Predicted uncertainty

3.3 MWI

3.3.1 MWI alone

Just 183 GHz channels, original noise

3.3.2 MWI and ICI

As in present version

3.4 AWS

\noindent 4 Discussion

\noindent 5 Conclusion

\newpage
\section{Data and methods}
